\section{Publications}

\subsection{“Shear Behavior of Fe/Fe\textsubscript{3}O\textsubscript{4} interfaces”. } Revista Materia V23-N2 (2018). Mariano Forti, Paula Alonso, Pablo Gargano, Gerardo Rubiolo. 

\subsection{“Properties of hexagonal Zr and tetragonal ZrO\textsubscript{2} low index surfaces from DFT calculations”. } Revista Materia V23-N2 (2018). Paula Alonso, Pablo Gargano, Laura Kniznik, Gerardo Rubiolo. 

\subsection{“Concentration of constitutional and thermal defects in UAl\textsubscript{4} ” Journal of Nuclear Materials 478 (2016) 74-82. } Pablo Gargano, Laura Kniznik, Paula Alonso, Mariano Forti, Gerardo Rubiolo.

\subsection{“A DFT study of atomic structure and adhesion at the Fe(BCC)/Fe\textsubscript{3} O\textsubscript{4} interfaces”. } Surface Science 647 (2016) 55–65. Mariano Forti, Paula Alonso, Pablo Gargano,Perla Balbuena, Gerardo Rubiolo.

\subsection{“Charge difference calculation in Fe/Fe\textsubscript{3}O\textsubscript{4} interfaces from DFT results”. } Procedia Materials Science 8 (2015) pp 1066 – 1072. Diego Tozini, Mariano Forti, Paula Alonso, Pablo Gargano, Gerardo Rubiolo.

\subsection{“Adhesion Energy of the Fe(BCC)/Magnetite Interface within the DFT approach”. } Procedia Materials Science 9 (2015) pp 612 – 618. Diego Tozini, Mariano Forti, Pablo Gargano, Paula Alonso, Gerardo Rubiolo. 

\subsection{“Ab-initio studies on carburization of Fe\textsubscript{3} Al based alloys”. } Procedia Materials Science 1 (2012) 191 – 198. Mariano Forti, Perla Balbuena, Paula Alonso.

 \subsection{“First principles study of U-Al system ground state”. } Procedia Materials Science 1 (2012) 514 –519. Laura Kniznik, Paula R. Alonso, Pablo H. Gargano, Mariano D. Forti, Gerardo H. Rubiolo.

\subsection{“Transition metals monoxides. } An LDA+U study”. Procedia Materials Science 1 (2012) 230 – 234. Mariano Forti, Paula R. Alonso, Pablo H. Gargano, Gerardo H. Rubiolo.

\subsection{“Electric and magnetic properties of PMMA/manganite composites”. } Physica B 404 (2009) 2760– 2762. Artale, C., Fermepin, S., Latino, M., Quintero, M., Granja, L., Sacanell, J., Polla G., Levy P. 

