\section{Research projects and third party funding}

\subsection{March 2025 - July 2026: Extension: Effect of composition on phase stability and mechanical properties of compositionally complex intermetallic phases. }
  Compute time allocation for a total of 4 million CPU hours at \href{https://pc2.uni-paderborn.de/}{Paderborn Center for Parallel Computing (PC2)}

  \subsection{March 2024 - March 2025: Effect of composition on phase stability and mechanical properties of compositionally complex intermetallic phases. }
  Compute time allocation for a total of 4 million CPU hours at \href{https://pc2.uni-paderborn.de/}{Paderborn Center
  for Parallel Computing (PC2)}

\subsection{January 2024 - Current: Artificial intelicence for intermetallic materials.}
German - French collaboration ANR DFG call 2022.
Coordinators: Thomas Hammerschmidt (\href{mailto:thomas.Hammerschmidt@icams.rub.de}{thomas. hammerschmidt@icams.rub.de}),
Jean Claude Crivello.

\subsection{September 2020 - December 2023: SFB/TR103: From atoms to turbine blades.}
German research fundation. 
Project coordinator: Gunther Eggeler. Adviser: Thomas Hammerschmidt (\href{mailto:thomas.Hammerschmidt@icams.rub.de}{thomas.hammerschmidt@icams.rub.de}).

\subsection{June 2020 - June 2023: Simulation and experiments on a proposed Zr alloy for hight burnup nuclear power plants.} 
Comisión Nacional de Energía Atómica, Agencia Nacional de Promoción Científica y Tecnológica, Ministerio de Ciencia, Técnica e innovación Productiva.
Principal Investigator: Dr, Paula Alonso (href{mailto:pralonso@cnea.gov.ar}{pralonso@cnea.gov.ar})

\subsection{February 2017 – February 2020: In the search for a new alloy for
fuel elements of the CAREM-25 Power Plant}, PICT-2015-2267. Comisión Nacional de
Energía Atómica, Agencia Nacional de Promoción Científica y Tecnológica,
Ministerio de Ciencia, Técnica e innovación Productiva.
Principal investigator: Dr. Gerardo Rubiolo (\href{mailto:rubiolo@cnea.gov.ar}{rubiolo@cnea.gov.ar}) 

\subsection{January 2017 – December 2019: In the search for a new alloy for fuel
elements of the CAREM-25 Power Plant, }Project 80020160500046SM. InstitutoSabato,
Universidad de San Martin, Comisión Nacional de Energía Atómica, Ministerio de
Ciencia, Técnica e Innovación Productiva. Principal investigator: Dr. Gerardo Rubiolo 
(\href{mailto:rubiolo@cnea.gov.ar}{rubiolo@cnea.gov.ar})

\subsection{August 2011- August 2015. Power Nuclear Reactor’s Materials
integrity. Atomistic / Continuum models applied to inter-diffusion in disperse
fuels and fracture in the oxide scales in steel pipes.} PICT-2011-1861 .
Ministerio de Ciencia, Técnica e Innovación Productiva. (\href{mailto:rubiolo@cnea.gov.ar}{rubiolo@cnea.gov.ar})

\subsection{January 2011 – December 2012. Pasivating oxide scale over iron},
Project UNSAM C063. Universidad Nacional de San Martin, Argentina. 
Principal investigator: Dr. Paula Alonso (href{mailto:pralonso@cnea.gov.ar}{pralonso@cnea.gov.ar})

 \subsection{January 2011 – December 2011. Constitutional Defects and Aluminum
 Migration Energy in UAl\textsubscript{4}}. Fundación Balseiro andComisión
 Nacional de Energía Atómica. Principal investigator: Gerardo Rubiolo (\href{mailto:rubiolo@cnea.gov.ar}{rubiolo@cnea.gov.ar})

\subsection{August 2010 – December 2015, Prespective studies, research and
development of technologies for nuclear power plants of the fourth generation}.
Comision Nacinoal de Energía Atómica. Principal investigator: Gerardo Rubiolo (\href{mailto:rubiolo@cnea.gov.ar}{rubiolo@cnea.gov.ar})

 \subsection{January 2010 - December 2012. Computational Methods applied to the
 study of physical and chemical properties of fuel elements in research
 reactors, and modeling of defect cluster migrations in technological
 materials}, CONICET. Principal investigator: Gerardo Rubiolo (\href{mailto:rubiolo@cnea.gov.ar}{rubiolo@cnea.gov.ar})

