\section{Invited talks}

\subsection{IMCPE-CNRS. Paris - France, 14th June 2023.} 
\emph{Data-based modelling of the structural stability of intermetallics}
(\href{https://www.icmpe.cnrs.fr/agenda/seminaire-du-dr-mariano-forti/}{https://www.icmpe.cnrs.fr})

\subsection{ Workshop en Procesamiento Físico Químico Avanzado. 11 – 15 March
	2014, Universidad Nacional de Santander.} Piedecuesta, Colombia. Invited
speaker. \emph{ a) “Vasp Workshop”},\emph{ b) “Mechanical Properties from DFT dCalculations”}.
%\href{http://www.sc3.uis.edu.co/pfqa-procesos-fisico-quimicos-avanzados/}{http://www.sc3.uis.edu.co/}.


\section{Participation in conferences}


\subsection{Intermetallics 2025 International Conference, September 29 to October 2, 2025}
\emph{Influence of partial occupancy on elastic constants of FeCr sigma phase}

\subsection{Materials Science: Modelling \& Design in Action!}
Workshop at NIMS, Tsukuba, Japan, 21-22 May 2024.
\emph{Machine-learning structural stability of complex intermetallic phases}

\subsection{TMS 2025 Annual Meeting \& Exhibition, 23-27 March 2025}
\emph{Machine-learning structural stability of complex intermetallic phases}
Forti, Drautz, Hammerschmidt.

\subsection{The 11th International Conference on Multiscale Materials Modeling, 23-26 September 2024}
\emph{Machine-learning structural stability of complex intermetallic phases}
Forti, Drautz, Hammerschmidt.

\subsection{17th. FEMS - Euromat, Frankfurt am Main, Germany, 03-07 September 2023.}
\emph{Comparison of atomic environment descriptors with domain knowledge of the interatomic bond }
Forti, Drautz, Hammerschmidt % (\href{https://euromat2023.com/program/scientific-program}{https://euromat2023.com})

\subsection{SFB/TR 103 Concluding simposium, 11-14 September 2023}
\emph{Highlight talk: "Data bases and machine learning"}

\subsection{86th DPG spring meeting of the condensed matter section, Dresden, Germany,  26-31 March 2023.}
\emph{Comparison of atomic environment descriptors with domain knowledge of the interatomic bond}
Forti, Drautz, Hammerschmidt. % (\href{https://www.dpg-verhandlungen.de/year/2023/conference/skm/part/mm/session/36/contribution/2}{https://www.dpg-verhandlungen.de/year/2023})

\subsection{85. DPG spring meeting, Regensburg, Germany,  4-9 September 2022.} Lecture,
\emph{Machine learning TCP phases with domain knowledge of the interatomic bond}
Forti, Burakovskaya, Drautz, and Hammerschmidt.
%(\href{https://www.dpg-verhandlungen.de/year/2022/conference/regensburg/part/o/session/83/contribution/3}{https://www.dpg-verhandlungen.de/year/2022})

\subsection{Workshop: "Research data management, machine learning and material informatics within the SFB/TR103" on line, 17th June 2021.}
\emph{Machine learning of DFT data and DFT databases}. Mariano Forti. 

\subsection{ 5th Nuclear Materials Conference, Elsevier – IAEA, 14-18 October
2018} Seattle, USA. Poster Presentations: \emph{ 1) “First-principles
thermodynamic study of point-defect structure and electrical conductivity in
tetragonal non-stoichiometric zirconia including lattice vibrations”} , Gargano,
Kniznik, Alonso, Forti, Rubuiolo. \emph{ 2) “DFT Study of the Early Stages of
Oxidation of the Zr(1010) Surface”} , F. Soto, M. Forti, P. Alonso, P. Gargano,
L. Kniznik, G. Rubiolo, P. Balbuena. \emph{ 3) “A DFT study of the resistance to
traction and shear loads of the Fe(BCC) / Fe\textsubscript{3}O\textsubscript{4}
interface”}, M.Forti, P. Alonso, P. Gargano, L. Kniznik, G. Rubiolo.
\href{https://elsevier.conference-services.net/programme.asp?conferenceID=4229&action=prog_list&session=45340}{https://elsevier.conference-services.net}

\subsection{16º SAM-CONAMET, November 2016} Córdoba, Argentina. \emph{“Shear
stress in Fe/Fe 3 O4 interfaces”. }Sociedad Argentina de Materiales.
%\href{http://sam-conamet2016.congresos.unc.edu.ar/}{http://sam-conamet2016.congresos.unc.edu.ar/}

\subsection{14th SAM-CONAMET, October 2014,} Santa Fe, Argentina. “Charge
difference calculation in Fe/Fe\textsubscript{3}O\textsubscript{4} interfaces
from DFT results”. Sociedad Argentina de Materiales.
%\href{http://www.unl.edu.ar/materiales2014/}{http://www.unl.edu.ar/materiales2014/}


\subsection{13th SAM-CONAMET, August 2013.} Sociedad Argentina de Materiales,
Puerto Iguazú, Misiones, Argentina “DFT Approximation to the Adhesion Energy of
the Fe(BCC)/Magnetite Interface”..

\subsection{XXXIX Reunión Anual de la Asociación Argentina de Tecnología
Nuclear, November 2012.}, Buenos Aires, Argentina.  \emph{ “Atomistic Model of
the Adhesion Problem in Magnetite /iron system”. }

\subsection{4º Meeting of young researchers in Cience And Technology, October
2012.}Sociedad Argentina de Materiales, Mar del Plata, Buenos Aires, Argentina.
\emph{  “Spin-Orbit Coupling effect on bandstructure of Iron monoxide in GGA+U
approximation”. }

\subsection{12th CONAMET/SAM, October 2012.}  Universidad Técnica Federico Santa
María, CONAMET-SAM, Valparaíso, Chile.\emph{“DFT study on adhesion energy in
Fe/Fe\textsubscript{3}O\textsubscript{4} interface”.}

\subsection{May 2012. 12th Anual Meeting of the Nuclear Fuel Division.} Centro
Atómico Constituyentes, Comisión Nacional de Energía Atómica. Buenos Aires,
Argentina.\emph{“Predicting toughness in Fe/Magnetite interfaces based in First
Principle calculations”.}

\subsection{PASI, January 2012.} Pan American Advanced Institute, Computational
Materials Science for Energy Generation and Conversion. Santiago De Chile,
Chile. %(Workshop, \url{http://www.cnf.cornell.edu/cnf\_pasi2012.html} ) 

\subsection{SAM / CONAMET 2011, October 2011.}  Rosario, Argentina. \emph{“Ab
Initio Studies on carburization in Fe\textsubscript{3}Al based alloys”}.
%(\url{http://www.ifir-conicet.gov.ar/SAM-ONAMET2011/documentos/topico6/215-161-1-SP.pdf}). 

\subsection{At The Frontiers of Condensed Matter IV, December 2008.} Centro
Atómico Constituyentes, Buenos Aires, Argentina. \emph{"Electric and Magnetic
properties of PMMA/Manganite composites". }

\subsection{RAFA, September 2008.} Reunión Anual de la Asociación de Física
Argentina, Salta, Argentina. \emph{"Electric and Magnetic properties of
PMMA/Manganite composites". }

