\section{Profesional Experience}

\subsection{February 2017 - Current: Researcher} at Comisión Nacional de Energía Atómica,  Gerencia Materiales. División Aleaciones Especiales. \textbf{} Advisor: Dr. Paula Alonso (\url{pralonso@cnea.gov.ar}). Position: Researcher. Density Functional Theory calculations in interfacial systems: Fe / Fe\textsubscript{3}O\textsubscript{4}, Zr/ZrO\textsubscript{2}. Point Defects in ZrO\textsubscript{2}. Linux System Administration in Desktop and Cluster Computers for High Performance Calculations. Daily use of Bash, Fortran and Python. Scientific support for Special Alloy Foundry including quality assurance.

\subsection{August 2010 – Current: Teaching assistant} at Instituto Sabato (UNSaM\-CNEA), Ayudante de 1ra. “Computer Simulation of Processes and Materials”. Professor: Ruben Weht (\url{ruweht@cnea.gov.ar}). In this course students make their own implementation of several numerical methods for solving differential equations including Finite Differences and Finite Elements.

\subsection{August 2010 – January 2017. Full Time Scolarship} at Comisión Nacional de Energía Atómica. Gerencia Materiales. División Aleaciones Especiales. , “ Ab\-Initio studies about adhesion in iron/magnetite interfaces”. Advisor: Dr. Paula Alonso (\url{pralonso@cnea.gov.ar}). Research and development activities. Linux System Administration in Desktop and Cluster Computers for High Performance Calculations. Daily use of Bash, Fortran and Python. 

\subsection{August 2006- August 2010. Full Time Scolarship } at Instituto de Tecnología Jorge Sabato (ITJS, UNSAM-CNEA). Materials Engineering. 

\subsection{January 2010 – July 2010. Intern } at Texas A\&M University, Department of Chemical Engineering. Final Work to get the Materials Engineering Degree. “Ab-Initio Studies about Carburization of Fe3Al Based Alloys”. Advisor: Dr. Perla Balbuena (\url{balbuena@tamu.edu}). 

\subsection{February 2008. Internship }at Gerencia Física, CNEA. “Synthesis and Mechanical Properties of Manganite / Polymer composites”. Reference: Griselda Polla (\url{grispoll@cnea.gov.ar})

\subsection{February 2007. Internship} at Condensed Matter Group, CNEA. “Eléctric and Magnetic Properties of Manganites/Polymer Composites”. Reference: Joaquín Sacanell (\url{sacanell@cnea.gov.ar}). 

